### 2019-03-15 papers/journal/experiments.tex
Vts dia update

\textbf{{\sattool (bounded model checker based tool)}}:
The $\fbmc$ encoding based on enumeration of paths (presented in section 6.2) for each variants of VTS is implemented in {\sattool}.
	%We have implemented the encodings for different variants of VTS (presented in section 6.2) using
The tool is based on CBMC, a successful bounded model checker, for C and C++ programs. 
%
%Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC
%
It verify property for all the possible states, up to a certain “depth,” a parametric limit on the size of the model.
%
The depth of model is specified by the user and can be  incrementally increased to a desired value.
%
%The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
%
%CBMC front end accepts

@@

\textbf{{\ourtool} (SMT and QBF based synthesis tool):}
\input{synth-table}
The synthesis encodings (presented in section 6.6) is implemented  in~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
%
The tool takes a partially defined VTS as input in a custom designed
input language.
%
The input is then converted to the constraints over VTS using the {\qbftool} interface. 
%
The tool can synthesize the queries discussed earlier and also their combinations.
%The tool can not only synthesize the discussed queries, but also their combinations.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.
%
The tool returns a complete VTS with visual graph representation as an output to the user.

>>>>

\textbf{{\sattool (Bounded model checker based tool)}}:
The $\fbmc$ encoding based on enumeration of paths (presented in section 6.2) for each variants of VTS is implemented in {\sattool}.
	%We have implemented the encodings for different variants of VTS (presented in section 6.2) using
The tool is based on CBMC, a successful bounded model checker, for C and C++ programs. 
%
%Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC
%
It verify property for all the possible states, up to a certain “depth,” a parametric limit on the size of the model.
%
The depth of model is specified by the user and can be  incrementally increased to a desired value.
%
%The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
%
%CBMC front end accepts

@@

\textbf{{\ourtool} (QBF based synthesis tool):}
\input{synth-table}
The synthesis encodings (presented in section 6.6) is implemented  in~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
%
The tool takes a partially defined VTS as input in a custom designed
input language.
%
The input is then converted to the constraints over VTS using the {\qbftool} interface. 
%
The tool can synthesize the queries discussed earlier and also their combinations.
%The tool can not only synthesize the discussed queries, but also their combinations.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.
%
The tool returns a complete VTS with visual graph representation as an output to the user.

### 2019-03-15 papers/journal/intro.tex
Minor corrections: 03
Updated the lang
Vts dia update

\begin{figure}
	\includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{diavts.png}
	\caption{Schematic of the vesicle transport system. Steps involved in vesicle transport between two compartments; a source and a target compartment are shown. 
	%
	The symbols used for different molecules involved in vesicle traffic are explained in the key. At the source compartment, transmembrane cargo proteins are sorted by cytosolic adaptor proteins. 
	%
	Here, the different colours indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming vesicle by adaptor proteins. 
	%
	Note here that a single type of coat protein can interact with multiple types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck by dynamin. 
	%
	Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex whose one end is attached to the target compartment. At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents into the target compartment.}
    \label{fig:vts}
\end{figure}

@@

\somya{schematic of snare regulatory network}
In keeping with their central role in vesicle transport,both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
%
\newline Sec17/18 bring about disassembly of SNARE complexes post-fusion in order that these SNAREs may be reused. 
\newline SM proteins have multiple modes of SNARE regulation: 
\begin{itemize}
	\item SM proteins can hold
	the Qa-SNAREs in an inhibited state and prevent or postpone their assembly into SNARE
	complexes.
	%
	\item Some SM proteins can act as a template upon which an early SNARE complex intermediate can
	form.
	%
	\item Finally, SM proteins bind the fully assembled
	SNARE complexes to protect them from premature disassembly by Sec17/18~\cite{baker2016chaperoning}.
	%
	\item SM proteins have also been shown to interact with tethers~\cite{yoon2018snare}.
\end{itemize}

\somya{schematic of intracellular compartments and  major routes}
\textbf{Major paths in the vesicle transport network}:
Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
%
\begin{itemize}
	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane( from where they are secreted out of the cell) via the Golgi apparatus\cite{alberts2002molecular}.
	%
	\item The endocytic route takes proteins from the outside of the cell, through the plasma membrane, to the endocytic compartments and the lysosome where they are digested. 
\end{itemize}
Other paths are used for cross talk between the secretory and the endocytic routes. For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes(endocytic route)\cite{progida2016bidirectional}. Also, recently, unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi apparatus. The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}.

@@

\subsubsection{Graph connectivity is an interesting and accessible property of the VTS}
\ankit{This section requires serious work and best written by Mukund.}
%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths. The molecules of the VTS, their interactions and modes of regulation have been worked out to a large extent through cell-biological experiments. But we do not know if this information is complete. In order to assess how completely we know the VTS, we need easily readable benchmarks.

\ankit{Need more clarity on the importance and relevance of the CONNECTIVITY and it's relevance.}
One such benchmark is provided by our result about connectivity of the VTS graph. Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected. For example, in a directed cyclic graph, every node has at least one incoming and one outgoing edge, at least 2 edges need to be removed in order to disconnect the graph. Therefore the underlying undirected graph is 2-connected. 
From our result, for a given set of biomolecular interactions, for a cell that is in steady state, we expect the VTS graph to have a certain k-connectivity. When regulation is given by arbitrary Boolean rules,   we find that VTS graphs must be 3-connected. And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2-strongly connected [28].

\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
\somya{But this is the para where we explain why connectivity is interesting an biological property}
The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%
In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%
These predictions are intended to be used as guides for future experiments. 
%
A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%
Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\

\ankit{Added this as a template. Will change it soon.}
\begin{example}
%
In figure~\ref{fig:M1}, we present a VTS that has 3 compartments and 8 molecules, and a corresponding pairing matrix.
%
Molecules are numbered 0-7.
%
In the VTS, labels are a string of molecule ids, and an overline over an id indicates that the molecule is active.
%
Every molecule on the node is active.
%
The activity of the molecules on an edge are controlled
by presence of the other molecules on the edge.
%
On the right side of the figure, we show the pairing matrix.
%
An entry 1 represents pairing between molecules.
%
$\times$ represents no pairing.
%
Rows corresponds to the labels of edges, and
columns corresponds to the labels of nodes.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 3-connected graph.
\end{example}

\input{pm-1-matrix}
%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}
%

@@

We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
%
We have applied our tool on several VTSs including
two found-in-nature VTSs.
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%

@@

%\textbf{Biological Model of VTS}
%

>>>>

%\includegraphics{akbar}

\begin{figure}
	\includegraphics[height=10cm,width=12cm]{diavts.eps}
	\caption{Schematic of the vesicle transport system. Steps involved in vesicle transport between two compartments; a source and a target compartment are shown. 
	%
	The symbols used for different molecules involved in vesicle traffic are explained in the key. At the source compartment, transmembrane cargo proteins are sorted by cytosolic adaptor proteins. 
	%
	Here, the different colours indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming vesicle by adaptor proteins. 
	%
	Note here that a single type of coat protein can interact with multiple types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck by dynamin. 
	%
	Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex whose one end is attached to the target compartment. At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents into the target compartment.}
    \label{fig:vts}
\end{figure}

@@

%\somya{schematic of snare regulatory network}
In keeping with their central role in vesicle transport, both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
%
Sec17/18 bring about disassembly of SNARE complexes post-fusion in order that these SNAREs may be reused. 
%
Whereas, SM proteins have following multiple modes of SNARE regulation: 
\begin{itemize}
	\item SM proteins can hold
	the Qa-SNAREs in an inhibited state and prevent or postpone their assembly into SNARE
	complexes.
	%
	\item Some SM proteins can act as a template upon which an early SNARE complex intermediate can
	form.
	%
	\item Finally, SM proteins bind the fully assembled
	SNARE complexes to protect them from premature disassembly by Sec17/18~\cite{baker2016chaperoning}.
	%
	\item SM proteins have also been shown to interact with tethers~\cite{yoon2018snare}.
\end{itemize}

%\somya{schematic of intracellular compartments and  major routes}
\textbf{Major paths in the vesicle transport network}:
Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
%
\begin{itemize}
	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane( from where they are secreted out of the cell) via the Golgi apparatus\cite{alberts2002molecular}.
	%
	\item The endocytic route takes proteins from the outside of the cell, through the plasma membrane, to the endocytic compartments and the lysosome where they are digested. 
\end{itemize}
Other paths are used for cross talk between the secretory and the endocytic routes. For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes(endocytic route)\cite{progida2016bidirectional}. Also, recently, unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi apparatus. The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}.

@@

\subsubsection{Graph connectivity is an interesting and accessible property of the VTS.} 
%\ankit{This section requires some rewrite and best written by Mukund.}
%\textbf{Properties of a VTS that satisfies all cell-biological constraints:}

Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths. The molecules of the VTS, their interactions and modes of regulation have been worked out to a large extent through cell-biological experiments. But we do not know if this information is complete. In order to assess how completely we know the VTS, we need easily readable benchmarks.

%\ankit{Need more clarity on the importance and relevance of the CONNECTIVITY and it's relevance.}
One such benchmark is provided by our result about connectivity of the VTS graph. Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected. For example, in a directed cyclic graph, every node has at least one incoming and one outgoing edge, at least 2 edges need to be removed in order to disconnect the graph. Therefore the underlying undirected graph is 2-connected. 
From our result, for a given set of biomolecular interactions, for a cell that is in steady state, we expect the VTS graph to have a certain k-connectivity. When regulation is given by arbitrary Boolean rules,   we find that VTS graphs must be 3-connected. And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2-strongly connected [28].

%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
%\somya{But this is the para where we explain why connectivity is interesting an biological property}
%\ankit{Yes; Both of our remark looks correct!}
The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%
In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%
These predictions are intended to be used as guides for future experiments. 
%
A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%
Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
%
%\ankit{Added this as a template. Will change it soon.}
\begin{example}
%
In figure~\ref{fig:M1}, we present a VTS that has 3 compartments and 8 molecules, and a corresponding pairing matrix.
%
Molecules are numbered 0-7.
%
In the VTS, labels are a string of molecule ids, and an overline over an id indicates that the molecule is active.
%
Every molecule on the node is active.
%
The activity of the molecules on an edge are controlled
by presence of the other molecules on the edge.
%
On the right side of the figure, we show the pairing matrix.
%
An entry 1 represents pairing between molecules.
%
$\times$ represents no pairing.
%
Rows corresponds to the labels of edges, and
columns corresponds to the labels of nodes.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 3-connected graph.
\end{example}
%
\input{pm-1-matrix}
%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}
%

@@

We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
%
We have applied our tool on several VTSs including
two found-in-nature VTSs.
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research. \\
%
%
%ankit{Added this as a template. Will change it soon.}
\begin{example}
	%
	In figure~\ref{fig:synth-vts}, we present a partial VTS that has 3 compartments and it's complete VTS by our tool. The synthesis is performed on the basis of steady state property and the  k-connectivity of the graph.

\end{example}
\input{synth-dia}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
~
